---
title: "COVID-19 Data by County"
author: "Patty Frontiera, UC Berkeley D-Lab"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

Row {data-height=900 .tabset .tabset-fade}
-------------------------------------

### Fatality Rate

```{r}
library(leaflet)
library(leaflet.esri)

# URL to access the JHU ESRI ArcGIS Online Layer
covid_esri_url = "https://services9.arcgis.com/6Hv9AANartyT7fJW/arcgis/rest/services/USCounties_cases_V1/FeatureServer/0"

# The popup content for all maps
the_popup = paste0("function(feature) {",
                        "x = feature.properties;",
		                    "temp = {Countyname: x.Countyname, ST_Abbr: x.ST_Abbr, \ 
                                Confirmed: x.Confirmed, Deaths: x.Deaths, \
                                FatalityRa: x.FatalityRa.toFixed(1), url: x.url, \ 
                                DateChecke: x.DateChecke} ;",
                        "  return L.Util.template(",
                        "    \"<p><b>{Countyname} County, {ST_Abbr}</b></br>",
                        "     <small><em>as of {DateChecke}</em></small></p>",
                        "      <p>Confirmed cases: {Confirmed} ",
                        "       <br>Deaths: {Deaths}",
                        "       <br>Fatality Rate: {FatalityRa}",
                        "      </p>",
                        "    \",",
                        "    temp",
                        "  );",
                        "}"
                      )

# map1 - fatality rate map
fatality_map <- leaflet() %>%
  
  # The the center point and zoom level for the map on startup
  setView(lng=-100.34004, lat=37.2855, zoom=5) %>%
  
  # Add a basemap
  addProviderTiles("CartoDB.Positron") %>%
  
  # Add the COVID-19 ESRI Layer
  addEsriFeatureLayer(covid_esri_url,
                      color = '#000000', 
                      weight = 0.25 , # thickness of the county outines
                      opacity = 0.65, # opacity of the county outlines
                      fillOpacity = 0.65,  # opacity of the county fill
                      highlightOptions = highlightOptions(weight=2, 
                                                          fillOpacity=0.8, 
                                                          bringToFront=TRUE,
                                                          sendToBack=TRUE),
                      options = featureLayerOptions(
                         simplifyFactor = 0.5,
                         precision = 5,
                         # Set the style based on the feature property we are mapping - here Fatality Rate (FatalityRa)
                         style = JS("function(feature){
                            var frate = feature.properties.FatalityRa;
                                 if (frate <= 0) {
                                    return {fillColor: 'white'};
                                 } else if (frate < 3){
                                    return {fillColor: 'yellow'};
                                 } else if (frate < 6){
                                    return {fillColor: 'orange'};
                                 } else {
                                    return {fillColor: 'red'};
                                 }
                          }")
                       ),
                      # Add the popup to the map
                      popupProperty = JS(the_popup)) %>%
  
  # Add a legend based on the property being mapped
  addLegend( title="Fatality Rate", 
             colors=c("white","yellow","orange","red"),
             labels=c("<1","1-3","3-6","6+"), 
             opacity=0.8, 
             position="bottomright")

# Display the map
fatality_map

```


### Confirmed Cases

```{r}
cases_map <- leaflet() %>%
  setView(lng=-100.34004, lat=37.2855, zoom=5) %>%
  addProviderTiles("CartoDB.Positron") %>%
  
  addEsriFeatureLayer(covid_esri_url,
                      color = '#000000', 
                      weight = 0.25 , # thickness of the county outines
                      opacity = 0.65, # opacity of the county outlines
                      fillOpacity = 0.65,  # opacity of the county fill
                      highlightOptions = highlightOptions(weight=2, 
                                                          fillOpacity=0.8, 
                                                          bringToFront=TRUE,
                                                          sendToBack=TRUE),
                      options = featureLayerOptions(
                        simplifyFactor = 0.5,
                        precision = 5,
                        style = JS("function(feature){
                          var frate = feature.properties.Confirmed;
                          if(frate <= 0){
                            return {fillColor: '#f1eef6'};
                          } else if(frate < 100){
                            return {fillColor: '#d7b5d8'};
                          } else if(frate < 500){
                            return {fillColor: '#df65b0'};
                          } else if(frate < 1000){
                            return {fillColor: '#dd1c77'};
                          } else {
                            return {fillColor: '#980043'};
                          }
                        }")),
                      
                      popupProperty = JS(the_popup)) %>%
  
  addLegend(title="Confirmed Cases", 
            colors=c('#980043','#dd1c77','#df65b0','#d7b5d8','#f1eef6'),
            labels=c("1000+","500-1000", "500-100", "1-100", "0"), 
            opacity=0.8, position="bottomright")



cases_map
```


### Confirmed Deaths

```{r}

deaths_map <- leaflet() %>%
  setView(lng=-100.34004, lat=37.2855, zoom=5) %>%
  addProviderTiles("CartoDB.Positron") %>%
  
  addEsriFeatureLayer(covid_esri_url,
                      color = '#000000', 
                      weight = 0.25 , # thickness of the county outines
                      opacity = 0.65, # opacity of the county outlines
                      fillOpacity = 0.65,  # opacity of the county fill
                      highlightOptions = highlightOptions(weight=2, 
                                                          fillOpacity=0.8, 
                                                          bringToFront=TRUE,
                                                          sendToBack=TRUE),
                      options = featureLayerOptions(
                        simplifyFactor = 0.5,
                        precision = 5,
                        style = JS("function(feature){
                          var frate = feature.properties.Deaths;
                          if(frate <= 0){
                            return {fillColor: '#f1eef6'};
                          } else if(frate < 50){
                            return {fillColor: '#d7b5d8'};
                          } else if(frate < 100){
                            return {fillColor: '#df65b0'};
                          } else if(frate < 500){
                            return {fillColor: '#dd1c77'};
                          } else {
                            return {fillColor: '#980043'};
                          }
                        }")),
                      
                      popupProperty = JS(the_popup)) %>%
            addLegend(title="Confirmed Deaths", 
            colors=c('#980043','#dd1c77','#df65b0','#d7b5d8','#f1eef6'),
            labels=c("500+","100-500", "50-100", "1-50", "0"), 
            opacity=0.8, position="bottomright")

deaths_map
```


Row {data-height=100}
-------------------------------------

### About the maps

This webmap contains the data on US COVID-19 cases aggregated by county. Updated daily, these data are pulled from an ESRI ArcGIS Online data layer created by the Center for Systems Science and Engineering (CSSE) at Johns Hopkins University. Details can be found [here](https://www.arcgis.com/home/item.html?id=4cb598ae041348fb92270f102a6783cb). The webmap was created for a tutorial by the [UC Berkeley D-Lab](https://dlab.berkeley.edu) using RStudio FlexDashboard, with the R packages leaflet and leaflet.esri and is for informational purposes only. The source code can be found [here](https://github.com/dlab-geo/webmaps).
 